---
title: "Lab10"
author: "J Bai"
date: "11/13/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Activity - Lab 10
### 1. Generate 1000 uniform pseudorandom variates using the runif() function.
```{r}
set.seed(123)
uniVars <- runif(1000)
# compute average and variance
mean(uniVars)
var(uniVars)

# compare your results with true mean and variance
# the true mean should be 1/2 * (0+1) = 0.5
# the true variance should be 1/12 * (1-0)^2 = 1/12 = 0.8333
```

### 2. Use the round() function together with runif() to generate 1000 pseudo-random integers which take values from 1 through 10. Use the table() function to check whether the observed frequencies for each value are close to what you expect.
```{r}
set.seed(123)
uniform.int <- ceiling(runif(1000, min=0, max=10))

table(uniform.int)
# the expected frequency: each one should have same frequency 100
```

### 3. Use sample() function to generate 1000 pseudo-random integers which take values from 1 through 10. Use the table() function to check whether the observed frequencies for each value are close to what you expect.
```{r}
set.seed(123)
random.int <- sample(1:10, 1000, replace = T)

table(random.int)
# the expected frequency: each one should have same frequency 100
```

### 4. Simulate 10000 binomial pseudo-random numbers with parameters 10 and 0.4. Let X be a Binomial(10, 0.4) random variable. Use the simulated numbers to estimate the following quantities:
```{r}
set.seed(999)
X.sample <- rbinom(10000, 10, 0.4)

# Pr(X <=3) 
sum(X.sample <= 3) / 10000

# Pr(X=3)
sum(X.sample == 3) / 10000

```

# Assignment - Lab 10
### 1. Write a function that calculates cumulative distribution function of a binomial random variable. Compare results from your function with pbinom() function.
```{r}
pbinom(-2, 23, 0.5)
```

```{r}
my_pbinom <- function(q, size, prob) {
  if(q >= size) { return(1) } 
  if(q < 0) { return(0) }
  q <- floor(q)
  res <- 0
  for(i in 0:q) {
    res <- res + choose(size, i) * prob^i * (1-prob)^(size-i)
  }
  return(res)
}

my_pbinom(-2, 23, 0.5)
```

### 2. Write a function that runs simulations to obtain power from a one-sample t-test. Run your function (with number of simulations = 10,000 ) with n = 30, delta = 0.5, sd = 1 and sig.level = 0.05. Compare your results with power.t.test(n = 30, delta = 0.5, sd = 1, sig.level = 0.05, type = 'one.sample')
```{r}
power.t.test(n = 30, delta = 0.5, sd = 1, sig.level = 0.05, type = 'one.sample')
```

```{r}
my_power <- function(n, delta, sd, sig.level = 0.05, simulations = 10000) {
  count <- replicate(simulations, {
    x <- rnorm(n, delta, sd)
    t.pv <- t.test(x)$p.value
    as.numeric(t.pv < sig.level)
  })
  t.power <- sum(count)/simulations
  return(t.power)
}

my_power(n = 30, delta = 0.5, sd = 1, sig.level = 0.05)
```


